
\begin{thebibliography}{9}

  \bibitem{1}
  \bibok{ Yang, B., Liu, Q., \& Liu, Y.}{: Recommender system: A comprehensive survey. Knowledge-Based Systems, 191, 105349, 2020}

  \bibitem{2}
  \bibok{ Prof. Dr. Ángel González-Prieto, \& Prof. Dr. Fernando Ortega}{: Special Issue "New Trends in Artificial Intelligence for Recommender Systems and Collaborative Filtering", A special issue of Applied Sciences, ISSN 2076-3417, 2022.}

  \bibitem{3}
  \bibok{ Zhou, T., Kusner, M. J., Zhao, S., Rush, A. M., \& Collins, M.}{: Deep contextualized word representations. In Proceedings of the 2018 Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies (pp. 2227-2237), 2018}


  \bibitem{4}
  \bibok{ Wenqi Fan, Yao Ma, Jiliang Tang et al.}{: Graph neural networks for social recommendation. IEEE Transactions on Knowledge and Data Engineering, 34(12), 2572-2585, 2021}


  \bibitem{5}
  \bibok{ Zhang, Shuai \& Yao, Lina \& Sun, Aixin \& Tay, Yi.}{: Deep Learning Based Recommender System: A Survey and New Perspectives. 10.1145/3285029, 2017 }

  \bibitem{6}
  \bibok{ He, X., Liao, L., Zhang, H., Nie, L., Hu, X., \& Chua, T. S.}{: Neural collaborative filtering. In Proceedings of the 26th International Conference on World Wide Web, pp. 173-182, 2017}

  %old refs
  \bibitem{1old}
  \bibok{ Qusai Shambour}{: A deep learning based algorithm for multi-criteria recommender systems, Knowledge-Based Systems, vol 211, 106545,Department of Software Engineering, Faculty of Information Technology, Al-Ahliyya Amman University, Amman, Jordan, 9 January 2021, doi: /10.1016/j.knosys.2020.106545}


  \bibitem{2old}
  \bibok{ Kim Falk}{: Practical Recommender Systems, Jan 18, 2019, isbn: 1617292702,978-1617292705}
  
  \bibitem{3old}
  \bibok{ Emre Yalcin, Alper Bilge}{: Investigating and counteracting popularity bias in group recommendations, Information Processing \& Management, vol 58, Issue 5, Computer Engineering Department, Sivas Cumhuriyet University, 58140 Sivas \& Akdeniz University, 07058 Antalya, Turkey, September 2021, 102608, doi: /10.1016/j.ipm.2021.102608}

  \bibitem{4old}
  \bibok{ Ken Shirriff}{: Hacker News, scoring, controversy, and penalties, Computer history, restoring vintage computers, 2020}

  \bibitem{5old}
  \bibok{ Huang, T. K., \& Lin, H. T.}{: Challenges and Techniques in Rating-based Recommender Systems. Journal of Ambient Intelligence and Humanized Computing, 10(5), 3659-3679. doi.org/10.1007/s12652-019-1211-1, 2019}


  \bibitem{6old}
  \bibok{ Guangxia Xu, Zhijing Tang, Chuang Ma, Yanbing Liu, Mahmoud Daneshmand}{: "A Collaborative Filtering Recommendation Algorithm Based on User Confidence and Time Context", Journal of Electrical and Computer Engineering, vol. 2019, ID 7070487, 2019, doi.org/10.1155/2019/7070487}

  \bibitem{7}
  \bibok{ Francesco Ricci, Lior Rokach, Bracha Shapira}{: Recommender Systems Handbook, 1st, 2nd, 3rd editions, ID 3265533, 2022}

  \bibitem{8}
  \bibok{ Adomavicius, G., \& Tuzhilin, A.}{: Personalization technologies: A process-oriented perspective. ACM Transactions on Management Information Systems, 11(1), 1-5, 2020}

  \bibitem{9}
  \bibok{ Garcia-Recuero, A., Gallego-Sánchez, J., \& Sánchez-Anguix, V.}{: Advances in recommender systems: A review of current research and future trends. IEEE Access, 9, 17902-17923, 2021}

  \bibitem{10}
  \bibok{ Koren, Y., Bell, R., \& Volinsky, C.}{: Matrix factorization techniques for recommender systems. Computer, 42(8), 30-37, 2020}

  %\bibitem{11}
  %\bibok{ Liu, F., Sun, S., Liu, W., \& Tian, Q. A content-based recommendation algorithm for item cold start problem. IEEE Access, 9, 100444-100453, 2021}

  \bibitem{12}
  \bibok{ Wang, S., Yu, J., Wu, X., \& Lu, J.}{: Personalized recommender systems: A comprehensive review. Journal of Computational Science, 51, 101305, 2021}

  %\bibitem{13}
  %\bibok{ Ekstrand, M. D., O'Mahony, M. P., \& Almerekhi, H. Fairness in recommendation: Information retrieval meets algorithmic decision theory. Foundations and Trends® in Information Retrieval, 13(3-4), 355-484, 2020}

  %\bibitem{14}
  %\bibok{ Zhang, Y., Xie, Y., Zheng, X., Sun, G., \& Xie, X. Personalized recommendation algorithms based on user behavior analysis: A survey. Neurocomputing, 451, 225-239, 2021}

  %\bibitem{15}
  %\bibok{ Jannach et al. "Recommender Systems", In Chapter 3.3.1, edition 2020, 10.1007/978-3-030-49678-2.}

  \bibitem{16}
  \bibok{ Aggarwal, Charu}{: Recommender Systems: The Textbook. Springer International Publishing, 2018.}

  %\bibitem{17}
  %\bibok{ Zhang, Jianhua. "An Improved Collaborative Filtering Algorithm Based on User and Item Preferences." IEEE Access, vol. 9, 2021, pp. 17084-17092.}

  \bibitem{18}
  \bibok{ Fernández-Tobías, I., Cantador, I., \& Bellogín, A.}{: Exploiting Product Metadata for Cold-Start Recommendations: A Multi-Task Regression Approach. In Proceedings of the 28th ACM International Conference on Information and Knowledge Management (pp. 1383-1392). ACM. November, 2019.}

  \bibitem{19}
  \bibok{ Guo, J., Wang, X., Zhang, Y., He, X., \& Du, J.}{: Learning from multi-domain heterogeneous networks for collaborative filtering. In Proceedings of the 43rd International ACM SIGIR Conference on Research and Development in Information Retrieval (pp. 1021-1024). ACM, July, 2020.}

  \bibitem{20}
  \bibok{ Congcong Wang, M. O’Mahony}{: Evaluating Recommender Systems, BSc. (Hons.) in Computer Science, UCD School of Computer Science, University College Dublin, October 17, 2018}

  %\bibitem{21}
  %\bibok{ Ricci, F., Rokach, L., \& Shapira, B. Recommender systems handbook (Vol. 1). Springe, ed.2022}

  \bibitem{22}
  \bibok{ Lee, Juho, et al.}{: "A comprehensive study of deep matrix factorization methods for recommender systems." Proceedings of the 14th ACM Conference on Recommender Systems. 2020.}

  \bibitem{23}
  \bibok{ Golub, Gene H., and Charles F. Van Loan}{: "Matrix Computations." 4th Edition, Johns Hopkins University Press, ISBN 10: 1-4214-0859-7 (eb)}

  \bibitem{24}
  \bibok{ Xun Zhou, Jing He, Guangyan Huang, Yanchun Zhang}{: SVD-based incremental approaches for recommender systems, Journal of Computer and System Sciences
  Volume 81, Issue 4, June 2016, pp. 717-733, 10.1016/j.jcss.2016.11.016}

  %\bibitem{25}
  %\bibok{ Xiangnan He et al, "Neural Collaborative Filtering: A Survey and Practitioners Guide,2020, 10.1145/3397271}

  %\bibitem{26}
  %\bibok{ Beutel, Alex, et al. "Latent cross: Making use of context in recurrent recommender systems, " Proceedings of the 12th ACM Conference on Recommender Systems. 2018, 10.1145/3269206.3271781}

  %\bibitem{27}
  %\bibok{ Wang, X., Zhang, H., \& Liu, X. A survey of collaborative filtering for recommender systems based on machine learning. IEEE Access, 8, 21936-21952, 10.1109/ACCESS, 2020.2962058}

  %\bibitem{28}
  %\bibok{ Vishal Saraswat and Shashank Gupta, Regularization Techniques for Deep Learning Based Natural Language Processing, published in the journal SN Computer Science in 2021.}

  %\bibitem{29}
  %\bibok{ Seungwoo Kang, Sangkeun Park, Sechan Oh, and Jaewoo Kang. Regularizing Matrix Factorization Models with User and Item Embeddings for Recommendation. Information Sciences, Volume 589, 1 February 2022, Pages 304-320, doi:10.1016/j.ins.2021.09.042}

  %\bibitem{30}
  %\bibok{ Khaled Ammar and Haoyuan Zhang, Matrix Factorization Techniques for Recommender Systems. In Proceedings of the 2021 IEEE International Conference on Data Mining (ICDM), pp. 959-968. doi:10.1109/ICDM50108.2021.00110}

  \bibitem{31}
  \bibok{ Chen, Y.-J. and Wang, Y.-C.}{: A Survey on Matrix Factorization for Recommender Systems. IEEE Access, 7, 158390-158404, 2019, doi:10.1109/ACCESS.2019.2948257}

  %\bibitem{32}
  %\bibok{ Petros Drineas and Michael W. Mahoney. "Lectures on randomized numerical linear algebra". In: Matrix computations and sparse matrix techniques (2018): pp. 1-107. Available at: arxiv.org, abs, 1704.01064}

  %\bibitem{33}
  %\bibok{ Ivan Vasilev, Daniel Slater, Gianmario Spacagna, Peter Roelants, Valentino Zocca, "Python Deep Learning - Second Edition", January 2019, Publisher(s): Packt Publishing, ISBN: 9781789348460}

  %\bibitem{34}
  %\bibok{ Zhang, G.; Liu, Y.; Jin, X., A survey of autoencoder-based recommender systems, Frontiers of Computer Science (electronic) 14(1),2020, 14, 430–450., doi:10.1007/s11704-018-8052-6}
  
  \bibitem{35}
  \bibok{ Cao, S.; Yang, N.; Liu, Z.}{: Online news recommender based on stacked auto-encoder. In Proceedings of the 2017 IEEE/ACIS 16th International Conference on Computer and Information Science (ICIS), Wuhan, China, pp. 721–726, 24–26 May 2017. }

  \bibitem{36}
  \bibok{ Nurmaini, S.; Darmawahyuni, A.; Sakti Mukti, A.N.; Rachmatullah, M.N.; Firdaus, F.; Tutuko, B.}{:Deep Learning-Based Stacked Denoising and Autoencoder for ECG Heartbeat Classification. Electronics,  pp. 9,135, 2020,}
  
  \bibitem{37}
  \bibok{ Diana Ferreira, Sofia Silva 2, António Abelha, and José Machado}{:   Recommendation System Using Autoencoders, Algoritmi Research Center, Department of Informatics, University of Minho, Campus of Gualtar, 4710 Braga, Portugal, Appl. Sci. 2020, 10(16), 5510; doi: /10.3390/app10165510}

  \bibitem{38}
  \bibok{ Hinton, G.E.; Zemel, R.S.}{: Autoencoders, minimum description length and Helmholtz free energy. In Advances in Neural Information Processing Systems; MIT Press: Cambridge, MA, USA; pp. 3–10.}

  \bibitem{39}
  \bibok{ Robin Vogel, Michael Bendersky, and Donald Metzler}{: Autoencoders for Recommender Systems: Survey and New Perspectives, 2020}

  \bibitem{40}
  \bibok{ Ankush Kumar and Ram Gopal Raj}{: A Comparative Study of Deep Learning Models for Recommendation System, 2020}

  \bibitem{41}
  \bibok{ Taesik Gong and Joonseok Lee}{: Autoencoder-based Collaborative Filtering for Improving the Accuracy, Diversity, and Serendipity of Recommendations, 2019}

  \bibitem{42}
  \bibok{ Sedhain, Suvash and Menon, Aditya and Sanner, Scott and Xie, Lexing}{:AutoRec: Autoencoders Meet Collaborative Filtering, pp111-112, 2019, doi: 10.1145/2740908.2742726}

  \bibitem{43}
  \bibok{Xiangnan He, Hanwang Zhang, Min-Yen Kan, and Tat-Seng Chua}{: Dropout-based feature engineering for representation learning on knowledge graphs. In Proceedings of the 25th ACM SIGKDD International Conference on Knowledge Discovery \& Data Mining, 2019.}
   
  \bibitem{43}
  \bibok{ Xiangyong Liu \& Guojun Wang \& Md Zakirul Alam Bhuiyan}{: Personalised context-aware re-ranking in recommender system, Connection Science, vol 34, num 1, pp: 319-338, pub. Taylor \& Francis, 2022}

  \bibitem{44}
  \bibok{ Prokhorenkova, L., Gusev, G., Vorobev, A., Dorogush, A. V., \& Gulin, A.}{: CatBoost: unbiased boosting with categorical features. Advances in Neural Information Processing Systems (NIPS), 31, 6638-6648, 2018, doi: 10.5555/3327757.332776}

  \bibitem{45}
  \bibok{ A. Krizhevsky, I. Sutskever and G. E. Hinton}{: "ImageNet classification with deep convolutional neural networks", Commun. ACM, vol. 60, no. 6, pp. 84-90, May 2017.}

  \bibitem{46}
  \bibok{ K. He, X. Zhang, S. Ren and J. Sun}{: "Deep residual learning for image recognition", Proc. IEEE Conf. Comput. Vis. Pattern Recognit. (CVPR), pp. 770-778, Jun. 2016.}

  \bibitem{47}
  \bibok{ B. Zhang, M. Zhu, M. Yu, D. Pu and G. Feng}{: "Extreme Residual Connected Convolution-Based Collaborative Filtering for Document Context-Aware Rating Prediction," in IEEE Access, vol. 8, pp. 53604-53613, 2020, doi: 10.1109/ACCESS.2020.2981088.}

  \bibitem{48}
  \bibok{ David Foster}{: Generative Deep Learning: Teaching Machines to Paint, Write, Compose, and Play, O'Reilly Media, 2019, isbn: 9781492041948}

  \bibok{ Jan Schlüter}{: Restricted Boltzmann Machine Derivations, OFAI, Austrian Research Institute for Artificial Intelligence, 2015}

  \bibitem{50}
  \bibok{ Guido Montufar}{: Restricted Boltzmann Machines:Introduction and Review, arXiv:1806.07066v1, 19 Jun 2018}

  \bibitem{51}
  \bibok{Amir H. Payberah}{: Autoencoders and Restricted Boltzmann Machines, payberah@kth.se, KTH, Vetenskap och konst (Science and Art), Royal Institute of Technology, 27 November 2019}

  \bibitem{52}
  \bibok{Benyamin Ghojogh, Ali Ghodsi, Fakhri Karray, Mark Crowley}{: Restricted Boltzmann Machine and Deep Belief Network: Tutorial and Survey, Department of Electrical and Computer Engineering, Department of Statistics and Actuarial Science \& David R. Cheriton School of Computer Science, Machine Learning Laboratory \& Data Analytics Laboratory \& Centre for Pattern Analysis and Machine Intelligence, University of Waterloo, Waterloo, ON, Canada 6 Auguest 2022}

  \bibitem{53}
  \bibok{ Kelleher, John D., and Brian Tierney}{: "Machine Learning: An Artificial Intelligence Approach." 1st ed., CRC Press, 2018.}

  \bibitem{54}
  \bibok{ Goodfellow, I., Bengio, Y., \& Courville, A.}{: Deep learning (Vol. 1). MIT press, 2016.}

  \bibitem{55}
  \bibok{ S. Elfwing, E. Uchibe, K. Doya}{: Expected energy-based restricted Boltzmann machine for classification, Neural Networks, Vol. 64, 2015, Pages 29-38, ISSN 0893-6080, doi: /10.1016/j.neunet.2014.09.006.}

  \bibitem{56}
  \bibok{ Sangchul Oh, Abdelkader Baggag, \& Hyunchul Nha}{: Entropy, Free Energy, and Work of Restricted Boltzmann Machines, Qatar Environment and Energy Research Institute, Qatar Computing Research Institute, Hamad Bin Khalifa University, Qatar Foundation, 5825 Doha, Department of Physics, Texas A\&M University at Qatar, Education City, 23874 Doha, Qatar, Pub: 11 May 2020, doi: 10.3390/e22050538}

  \bibitem{57}
  \bibok{ Jin, Qibing \& Zhang, Hengyu \& Zhang, Yuming \& Cai, Wu \& Chi, Meixuan.}{: An improved parallel MDBN with AVMD for nonlinear system modeling. IEEE Access. 8. 1-1. 2020, doi: 10.1109/ACCESS.2020.2968508. }


  \bibitem{58}
  \bibok{ Yang, P., Varadharajan, S., Wilson, L.A. et al.}{: Parallelized Training of Restricted Boltzmann Machines Using Markov-Chain Monte Carlo Methods. SN COMPUT. SCI. 1, 165, 2020, doi: 10.1007/s42979-020-00170-7}

  \bibitem{59}
  \bibok{Ruslan Salakhutdinov, Andriy Mnih, Geoffrey Hinton}{: Restricted Boltzmann Machines for Collaborative Filtering, University of Toronto, 6 King’s College Rd., Toronto, Ontario M5S 3G4, Canada, origin 2007, cited by Bhuvaneshwari P, Rao A and Robinson Y. (2022). Top-N Recommendation System Using Explicit Feedback and Outer Product Based Residual CNN. Wireless Personal Communications. 10.1007/s11277-022-09984-5. 128:2. (967-983). Online publication d1-Jan-2023. \& al (2023)}


  \bibitem{60}
  \bibok{ Yongheng Mu \& Yun Wu}{: Multimodal Movie Recommendation System Using Deep Learning, mpdi, Mathematics, 2023, 11, 895, doi:10.3390/math11040895}
  
  \bibitem{61}
  \bibok{ Jena, K.K.; Bhoi, S.K.; Malik, T.K.; Sahoo, K.S.; Jhanjhi, N.Z.; Bhatia, S.; Amsaad, F.}{: E-Learning Course Recommender System Using Collaborative Filtering Models. Electronics, 2023, 12, 157. doi:10.3390/electronics12010157}

  \bibitem{62}
  \bibok{ Dou, R., Arslan, O., \& Zhang, C.}{: Biased autoencoder for collaborative filtering with temporal signals. Expert Systems with Applications, 2021, 186, 115775, doi:10.1016/j.eswa.2021.115775}

  \bibitem{63}
  \bibok{Bobadilla, J.; Alonso, S.; Hernando, A.}{: Deep Learning Architecture for Collaborative Filtering Recommender Systems. Appl. Sci. 2020, 10, 2441. https://doi.org/10.3390/app10072441}

  \bibitem{64}
  \bibok{ Team Members : JH (Janghyun) Baek, John Tsai, Justin Shamoun, Muriel Marable, Ying Cui, Advisors: Ilkay Altintas, Julian McAuley}{: Amazon Recommender System, University of California San Diego, 2021,}

  \bibitem{65}
  \bibok{Smirnova, E., Tsymbalov, E., \& Kalinin, A.}{: A. Deep matrix factorization for recommender systems. In Proceedings of the 14th International Conference on Web and Social Media, pp. 732-733, 2020.}

  \bibitem{66}
  \bibok{James Bennett and Stan Lanning}{: The Netflix Prize, Bennett2007TheNP, 2009}

  \bibitem{67}
  \bibok{ GM Harshvardhan, Mahendra Kumar Gourisaria, Siddharth Swarup Rautaray, Manjusha Pandey}{: UBMTR: Unsupervised Boltzmann machine-based time-aware recommendation system, Journal of King Saud University - Computer and Information Sciences, Vol. 34, Issue 8, Part B, pp: 6400-6413, 2022, ISSN 1319-1578,  doi: /10.1016/j.jksuci.2021.01.017.}

  \bibitem{68}
  \bibok{ D. Yang, J. Zhang, S. Wang, X. Zhang}{: A time-aware CNN-based personalized recommender system, Complexity, 1–11, 2019, doi: 10.1155/2019/9476981}
\end{thebibliography}
